Fourier-domain modulations and delays of gravitational-wave signals

### 2017-12-20 docs/paper_method.tex
Edits to the paper.

The authors of~\cite{KCY14} then proposed a resummation scheme for~\eqref{eq:resultdffPsiTf}, using finite differences for the derivatives. Indeed, the result~\eqref{eq:resultdffPsiTf} looks like a symmetrized Taylor expansion, except for the factors $i^{p}$ and $1/p!$ instead of $1/(2p)!$. Truncating the sum at some finite order $N$, one can write (following~\cite{KCY14})
\be\label{eq:stencilresult}
	\calT_{\rm phase}(f) \simeq \sum\limits_{p = 0}^{N} \frac{(-i\epsilon\Tf^{2})^{p}}{2^{p}p!} \partial_{t}^{2p}F(\tf) \simeq \calF_{\Tf}^{N,\epsilon}[F] (\tf) \,,
\ee
with the operator $\calF_{T}^{N,\epsilon}$ defined as
\be\label{eq:stencilfresnel}
	\calF_{T}^{N,\epsilon}[F] (t) \equiv \frac{1}{2}\sum\limits_{k=0}^{N} a_{N,k}^{\epsilon} \left( F(t + kT) + F(t - k T) \right) \,,
\ee
provided that the complex coefficients $a_{N,k}^{\epsilon}$ are a solution of the $N+1$-dimensional linear system~\cite{KCY14}
\be\label{eq:stencilsystem}
	(-i\epsilon)^{p} (2p-1)!! = \sum\limits_{k=0}^{N} a_{N,k}^{\epsilon} k^{2p} \quad \text{for } p=0,\dots,N \,.
\ee
In~\cite{KCY14}, only the case $\epsilon=1$ was considered. The two solutions for the stencil coefficients in the two cases $\epsilon = \pm 1$ are simply related by a complex conjugation. Explicit expressions for the stencil coefficients $a_{N,k}^{\epsilon}$ are given in App.~\ref{app:stencil} for the first values of $N$.

@@

We can give an alternative interpretation of the expansion~\eqref{eq:resultdffPsiTf} and of Sec.~\ref{subsec:resumquadphase} in terms of the Fresnel transform. For simplicity of notation, here we keep to the case of a pure modulation $F$ with no delays, $d=0$. We will reintroduce the delays below in Sec.~\ref{subsec:delays}. To obtain~\eqref{eq:resultdffPsiTf}, we expanded fully the exponential of the phase as a Taylor series. If it is not expanded, however, we have
\be\label{eq:integralquadphase}
	\tilde{s}(f)	\simeq \tilde{h}(f) \int \ud t\, F(t) \int\ud f'\, e^{2i\pi f' (t-\tf)} \exp\left[ 2i\pi^{2} \epsilon{f'}^{2} \Tf^{2} \right] \,,
\ee
where we recall that $\epsilon = -\mathrm{sgn}(\ud ^{2} \Psi/\ud f^{2})$. The integral on $f'$ is a simple complex Gaussian integral, and results in a complex Gaussian integral over time where we recognize a Fresnel transform~\cite{} \SM{[C]} of the function $F$. We introduce for the Fresnel transform the notation
\be\label{eq:defFresnel}
	\calF_{\tau}[F](t_{0}) \equiv \frac{e^{i\frac{\pi}{4}}}{\sqrt{2\pi} \tau} \int \ud t \, \exp\left[ - \frac{i}{2} \left( \frac{t-t_{0}}{\tau} \right)^{2}\right] F(t) \,,
\ee
together with the additional notation
\be\label{eq:Fresnelsign}
	\calF^{\epsilon}_{\tau}[F](t_{0}) \equiv
\begin{cases}
	 \calF_{\tau}[F](t_{0}) &\text{ if } \epsilon=1 \\
	 \calF_{\tau}[F^{*}](t_{0})^{*} &\text{ if } \epsilon=-1
\end{cases}
\ee
to accomodate for the possible sign change represented by $\epsilon$. The integral~\eqref{eq:integralquadphase} then gives for the transfer function
\be\label{eq:resultFresnel}
	\calT_{\rm phase}(f) = \calF^{\epsilon}_{\Tf}[F](\tf) \,.
\ee

@@

Thus, the previous result~\eqref{eq:stencilresult}-\eqref{eq:stencilfresnel} can be rephrased as a quadrature rule, and the stencil $\calF_{T}^{N,\epsilon}$ is an quadrature approximation of the Fresnel transfrom $\calF^{\epsilon}_{T}$. If one allows for polynomial integrands\footnote{Note that such integrals with a polynomial integrand are formally divergent. One can regularize them for instance by introducing a small imaginary part in $\tau$ that is sent it to $0$ at the end of the computation.} in~\eqref{eq:defFresnel}, using the stencil~\eqref{eq:stencilfresnel} amounts to building a quadrature rule for the particular choice of nodes $\tf \pm k \Tf$, which is exact (with a regularization) if $F$ is a symmetric polynomial of degree $\leq 2N$. As a verification, performing a formal Taylor expansion in time of $F(t)$ around $\tf$ in the integral~\eqref{eq:defFresnel} and integrating term by term yields back~\eqref{eq:resultdffPsiTf}.

@@

Next, we consider the case where the quadratic phase correction is kept as well, as in Sec.~\ref{subsec:fresneltransform}. Keeping as before only the first-order terms in $\dot{d}$ (and neglecting its higher derivatives), we can write
\begin{widetext}
\begin{align}
	\tilde{s}(f) &\simeq \tilde{h}(f) \int \ud t \, F(t) e^{-2i\pi f d(t)} \int \ud f' \, \exp\left[ 2i\pi \epsilon \Tf^{2} f'^{2} + 2i\pi f' (t+d(t) - \tf) \right] \nn\\
	&\simeq \tilde{h}(f) \frac{e^{i\epsilon\frac{\pi}{4}}}{\sqrt{2\pi}\Tf} \int \ud \tau \, \frac{F(\tau - d(\tau))}{1+\dot{d}(\tau)} e^{-2i\pi f d(\tau)(1-\dot{d}(\tau))}\exp\left[ -\frac{i\epsilon}{2} \frac{(\tau - \tf)^{2}}{\Tf^{2}} \right] \,,
\end{align}
where we used a change of variable $\tau = t_{d}(t)$. We see that the result can again be expressed as a Fresnel transform. When considering amplitude corrections as well, as in~\eqref{eq:resulttaylorA}, additional powers of $f'$ can be translated as time derivatives with respect to the variable $\tau$ after performing the change of variables. This produces the final result:
\be\label{eq:transferfinal}
	\calT(f) = \sum\limits_{k \geq 0} \frac{(-i)^{k}}{k!} (T_{Ak})^{k} \calF^{\epsilon}_{\Tf} \left[ \frac{\ud^{k}}{\ud \tau^{k}} \left( \frac{F(\tau - d(\tau))}{1+\dot{d}(\tau)} e^{-2i\pi f d(\tau)(1-\dot{d}(\tau))} \right) \right] (\tf) \,.
\ee
\end{widetext}

@@

In this result, the Fresnel transform $\calF^{\epsilon}_{\Tf}$ can in turn be approximated by the stencil $\calF^{N,\epsilon}_{\Tf}$ using the formula~\eqref{eq:stencilfresnel}. The timescales $\Tf$ and $T_{Ak}$ were defined in~\eqref{eq:defTf} and~\eqref{eq:defTA}, and the generalized time-to-frequency function $t_{f}$ was given in~\eqref{eq:deftf}. The delays $d$ are present only in the LISA context, while in the context of precessing binaries we only have to consider the modulation function $F$. In practice, only the first few of the terms in the series expansion are relevant. We will investigate several orders of approximation, combining corrections from the phase, amplitude and delays, and explore which ones are relevant for a given level of accuracy. We will use symbols of the form $\{N,A,d\}$ to indicate the order of the stencil in~\eqref{eq:stencilfresnel}, the maximal order of the amplitude correction included, and the inclusion or not of the delay corrections.

In the LISA context, due to the smallness of the corrections we will only go up to $k=1$ in~\eqref{eq:transferfinal}, and in computing the remaining time derivatives in~\eqref{eq:transferfinal} we will neglect the second and higher derivatives. We will also use $F(\tau - d(\tau)) \simeq (F - d \dot{F})(\tau)$. This gives concretely:
\begin{widetext}
\begin{subequations}
\begin{align}
	\{N,A:0,d:0\}&: \; \calT(f) = \calF^{\epsilon}_{\Tf} \left[ F e^{-2i\pi f d} \right] (t_{f}) \,, \\
	\{N,A:1,d:0\}&: \; \calT(f) = \calF^{\epsilon}_{\Tf} \left[ \left(F - i T_{A1} \left( \dot{F} - 2i\pi f \dot{d}\right) \right) e^{-2i\pi f d} \right] (t_{f}) \,, \\
	\{N,A:0,d:1\}&: \; \calT(f) = \calF^{\epsilon}_{\Tf} \left[ \frac{F - d\dot{F}}{1+\dot{d}} e^{-2i\pi f d (1-\dot{d})} \right] (t_{f})\,, \\
	\{N,A:1,d:1\}&: \; \calT(f) = \calF^{\epsilon}_{\Tf} \left[ \frac{1}{1+\dot{d}}\left(  F - d\dot{F} - i T_{A1} \left( \dot{F} - 2i\pi f \dot{d} \right) \right) e^{-2i\pi f d (1 - \dot{d})} \right] (t_{f})\,.
\end{align}
\end{subequations}
\end{widetext}

In the context of precessing binaries, the delays are absent and we will go up to $k=2$ in~\eqref{eq:transferfinal}. The tranfer function at different orders of approximation will be:
\begin{subequations}
\begin{align}
	\{N,A:0\}&: \; \calT(f) = \calF^{\epsilon}_{\Tf} \left[ F \right] (t_{f}) \,, \\
	\{N,A:1\}&: \; \calT(f) = \calF^{\epsilon}_{\Tf} \left[ \left(F - i T_{A1} \dot{F} \right) \right] (t_{f}) \,, \\
	\{N,A:2\}&: \; \calT(f) = \calF^{\epsilon}_{\Tf} \left[ \left(F - i T_{A1} \dot{F} - \frac{1}{2} (T_{A2})^{2} \ddot{F} \right) \right] (t_{f}) \,.
\end{align}
\end{subequations}

In the following, it will be convenient to introduce error estimates built from the Taylor-like series~\eqref{eq:resulttaylorPsi},~\eqref{eq:resulttaylorA} and~\eqref{eq:resulttaylordelay}. We simply define  this error estimates at a certain level of approximation as the magnitude of the first term ignored in the original Taylor series. Thus we define, with $G(f,t) = F(t) e^{-2i\pi f d(t)}$,
\begin{subequations}\label{eq:deffom}
\begin{align}
	\epsilon_{\Psi 2} &\equiv \frac{1}{2} \Tf^{2} \left| \frac{1}{G}\partial_{tt}G \right| \,, \\
	\epsilon_{A 1} &\equiv T_{A1} \left| \frac{1}{G} \partial_{t} G \right| \,, \\
	\epsilon_{A 2} &\equiv \frac{1}{2} T_{A2}^{2} \left| \frac{1}{G} \partial_{tt}G \right| \,, \\
	\epsilon_{d} &\equiv \frac{1}{2\pi} \left| \frac{1}{G} \partial_{tf} G \right| \,,
\end{align}
\end{subequations}
where the function $G$ and its derivatives are evaluated at $(f, t_{f})$. Reaching $\epsilon \simeq 1$ will indicate a breakdown of the perturbative approach.

@@

Using the Newtonian-order expressions~\eqref{eq:timescalesN} for the signal-dependent timescales $\Tf$ and $T_{A1}$, we can obtain a useful order-of-magnitude estimate for the error measures $\epsilon$ introduced in~\eqref{eq:deffom}. Higher-order amplitude terms beyond the first one in~\eqref{eq:resulttaylorA} will turn out to be completely negligible in the LISA case and we will ignore them in the following. We will present these estimates separately for the orbital response~\eqref{eq:transferOlocal} and the constellation~\eqref{eq:transferclocal}, as the different baseline of the delays ($R$ or $L$) as well as the presence of a time-varying prefactor $F(t)$ both affect the result. As we will see, when estimating the magnitude of the relevant derivatives of $G$ we have to take into account delay factors of the type $2\pi f d$.

@@

\subsection{Direct approach for periodic modulations and delays}\label{subsec:comblisa}

In the LISA case, the modulations and delays entering~\eqref{eq:yslr} are periodic, with a period of $f_{0} = 1/\mathrm{yr} \simeq 3.2\times 10^{-8}\mathrm{Hz}$. If the above perturbative formalism cannot be applied, we can still exploit this periodic structure . \SM{[]}
\be
	G(f,t) = \sum_{n} c_{n}(f) e^{-in\Omega_{0}t} \,.
\ee

>>>>

The authors of~\cite{KCY14} then proposed a resummation scheme for~\eqref{eq:resultdffPsiTf}, using finite differences for the derivatives. Indeed, the result~\eqref{eq:resultdffPsiTf} looks like a symmetrized Taylor expansion, except for the factors $i^{p}$ and $1/p!$ instead of $1/(2p)!$. Truncating the sum at some finite order $N$, one can write (following~\cite{KCY14})
\be\label{eq:stencilresult}
	\calT_{\rm phase}(f) \simeq \sum\limits_{p = 0}^{N} \frac{(-i\epsilon\Tf^{2})^{p}}{2^{p}p!} \partial_{t}^{2p}F(\tf) \simeq \calF^{N}_{\Tf, \epsilon}[F] (\tf) \,,
\ee
with the operator $\calF_{T, \epsilon}^{N}$ defined as
\be\label{eq:stencilfresnel}
	\calF_{T, \epsilon}^{N}[F] (t) \equiv \frac{1}{2}\sum\limits_{k=0}^{N} a_{N,k}^{\epsilon} \left( F(t + kT) + F(t - k T) \right) \,,
\ee
provided that the complex coefficients $a_{N,k}^{\epsilon}$ are a solution of the $N+1$-dimensional linear system~\cite{KCY14}
\be\label{eq:stencilsystem}
	(-i\epsilon)^{p} (2p-1)!! = \sum\limits_{k=0}^{N} a_{N,k}^{\epsilon} k^{2p} \quad \text{for } p=0,\dots,N \,.
\ee
In~\cite{KCY14}, only the case $\epsilon=1$ was considered. The two solutions for the stencil coefficients in the two cases $\epsilon = \pm 1$ are simply related by a complex conjugation. Explicit expressions for the stencil coefficients $a_{N,k}^{\epsilon}$ are given in App.~\ref{app:stencil} for the first values of $N$.

@@

We can give an alternative interpretation of the expansion~\eqref{eq:resultdffPsiTf} and of Sec.~\ref{subsec:resumquadphase} in terms of the Fresnel transform. For simplicity of notation, here we keep to the case of a pure modulation $F$ with no delays, $d=0$. We will reintroduce the delays below in Sec.~\ref{subsec:delays}. To obtain~\eqref{eq:resultdffPsiTf}, we expanded fully the exponential of the phase as a Taylor series. If it is not expanded, however, we have
\be\label{eq:integralquadphase}
	\tilde{s}(f)	\simeq \tilde{h}(f) \int \ud t\, F(t) \int\ud f'\, e^{2i\pi f' (t-\tf)} \exp\left[ 2i\pi^{2} \epsilon{f'}^{2} \Tf^{2} \right] \,,
\ee
where we recall that $\epsilon = -\mathrm{sgn}(\ud ^{2} \Psi/\ud f^{2})$. The integral on $f'$ is a simple complex Gaussian integral, and results in a complex Gaussian integral over time where we recognize a Fresnel transform~\cite{} \SM{[C]} of the function $F$. We introduce for the Fresnel transform the notation
\be\label{eq:defFresnel}
	\calF_{\tau}[F](t_{0}) \equiv \frac{e^{i\frac{\pi}{4}}}{\sqrt{2\pi} \tau} \int \ud t \, \exp\left[ - \frac{i}{2} \left( \frac{t-t_{0}}{\tau} \right)^{2}\right] F(t) \,,
\ee
together with the additional notation
\be\label{eq:Fresnelsign}
	\calF_{\tau, \epsilon}[F](t_{0}) \equiv
\begin{cases}
	 \calF_{\tau}[F](t_{0}) &\text{ if } \epsilon=1 \\
	 \calF_{\tau}[F^{*}](t_{0})^{*} &\text{ if } \epsilon=-1
\end{cases}
\ee
to accomodate for the possible sign change represented by $\epsilon$. The integral~\eqref{eq:integralquadphase} then gives for the transfer function
\be\label{eq:resultFresnel}
	\calT_{\rm phase}(f) = \calF_{\Tf, \epsilon}[F](\tf) \,.
\ee

@@

Thus, the previous result~\eqref{eq:stencilresult}-\eqref{eq:stencilfresnel} can be rephrased as a quadrature rule, and the stencil $\calF_{T, \epsilon}^{N}$ is an quadrature approximation of the Fresnel transfrom $\calF_{T, \epsilon}$. If one allows for polynomial integrands\footnote{Note that such integrals with a polynomial integrand are formally divergent. One can regularize them for instance by introducing a small imaginary part in $\tau$ that is sent it to $0$ at the end of the computation.} in~\eqref{eq:defFresnel}, using the stencil~\eqref{eq:stencilfresnel} amounts to building a quadrature rule for the particular choice of nodes $\tf \pm k \Tf$, which is exact (with a regularization) if $F$ is a symmetric polynomial of degree $\leq 2N$. As a verification, performing a formal Taylor expansion in time of $F(t)$ around $\tf$ in the integral~\eqref{eq:defFresnel} and integrating term by term yields back~\eqref{eq:resultdffPsiTf}.

@@

Next, we consider the case where the quadratic phase correction is kept as well, as in Sec.~\ref{subsec:fresneltransform}. Keeping as before only the first-order terms in $\dot{d}$ (and neglecting its higher derivatives), we can write
\begin{widetext}
\begin{align}
	\tilde{s}(f) &\simeq \tilde{h}(f) \int \ud t \, F(t) e^{-2i\pi f d(t)} \int \ud f' \, \exp\left[ 2i\pi \epsilon \Tf^{2} f'^{2} + 2i\pi f' (t+d(t) - \tf) \right] \nn\\
	&\simeq \tilde{h}(f) \frac{e^{i\epsilon\frac{\pi}{4}}}{\sqrt{2\pi}\Tf} \int \ud \tau \, \frac{F(\tau - d(\tau))}{1+\dot{d}(\tau)} e^{-2i\pi f d(\tau)(1-\dot{d}(\tau))}\exp\left[ -\frac{i\epsilon}{2} \frac{(\tau - \tf)^{2}}{\Tf^{2}} \right] \,,
\end{align}
where we used a change of variable $\tau = t_{d}(t)$. We see that the result can again be expressed as a Fresnel transform. When considering amplitude corrections as well, as in~\eqref{eq:resulttaylorA}, additional powers of $f'$ can be translated as time derivatives with respect to the variable $\tau$ after performing the change of variables. This produces the final result:
\be\label{eq:transferfinal}
	\calT(f) = \sum\limits_{k \geq 0} \frac{(-i)^{k}}{k!} (T_{Ak})^{k} \calF_{\Tf, \epsilon} \left[ \frac{\ud^{k}}{\ud \tau^{k}} \left( \frac{F(\tau - d(\tau))}{1+\dot{d}(\tau)} e^{-2i\pi f d(\tau)(1-\dot{d}(\tau))} \right) \right] (\tf) \,.
\ee
\end{widetext}

@@

In this result, the Fresnel transform $\calF^{\epsilon}_{\Tf}$ can in turn be approximated by the stencil $\calF^{N}_{\Tf, \epsilon}$ using the formula~\eqref{eq:stencilfresnel}. The timescales $\Tf$ and $T_{Ak}$ were defined in~\eqref{eq:defTf} and~\eqref{eq:defTA}, and the generalized time-to-frequency function $t_{f}$ was given in~\eqref{eq:deftf}. The delays $d$ are present only in the LISA context, while in the context of precessing binaries we only have to consider the modulation function $F$. In practice, only the first few of the terms in the series expansion are relevant. We will investigate several orders of approximation, combining corrections from the phase, amplitude and delays, and explore which ones are relevant for a given level of accuracy. We will use symbols of the form $\{N,A,d\}$ to indicate the order of the stencil in~\eqref{eq:stencilfresnel}, the maximal order of the amplitude correction included, and the inclusion or not of the delay corrections.

In the LISA context, due to the smallness of the corrections we will only go up to $k=1$ in~\eqref{eq:transferfinal}, and in computing the remaining time derivatives in~\eqref{eq:transferfinal} we will neglect the second and higher derivatives. We will also use $F(\tau - d(\tau)) \simeq (F - d \dot{F})(\tau)$. This gives concretely:
\begin{widetext}
\begin{subequations}
\begin{align}
	\{N,A:0,d:0\}&: \; \calT(f) = \calF^{N}_{\Tf, \epsilon} \left[ F e^{-2i\pi f d} \right] (t_{f}) \,, \\
	\{N,A:1,d:0\}&: \; \calT(f) = \calF^{N}_{\Tf, \epsilon} \left[ \left(F - i T_{A1} \left( \dot{F} - 2i\pi f \dot{d}\right) \right) e^{-2i\pi f d} \right] (t_{f}) \,, \\
	\{N,A:0,d:1\}&: \; \calT(f) = \calF^{N}_{\Tf, \epsilon} \left[ \frac{F - d\dot{F}}{1+\dot{d}} e^{-2i\pi f d (1-\dot{d})} \right] (t_{f})\,, \\
	\{N,A:1,d:1\}&: \; \calT(f) = \calF^{N}_{\Tf, \epsilon} \left[ \frac{1}{1+\dot{d}}\left(  F - d\dot{F} - i T_{A1} \left( \dot{F} - 2i\pi f \dot{d} \right) \right) e^{-2i\pi f d (1 - \dot{d})} \right] (t_{f})\,.
\end{align}
\end{subequations}
\end{widetext}

In the context of precessing binaries, the delays are absent and we will go up to $k=2$ in~\eqref{eq:transferfinal}. The tranfer function at different orders of approximation will be:
\begin{subequations}
\begin{align}
	\{N,A:0\}&: \; \calT(f) = \calF^{N}_{\Tf, \epsilon} \left[ F \right] (t_{f}) \,, \\
	\{N,A:1\}&: \; \calT(f) = \calF^{N}_{\Tf, \epsilon} \left[ \left(F - i T_{A1} \dot{F} \right) \right] (t_{f}) \,, \\
	\{N,A:2\}&: \; \calT(f) = \calF^{N}_{\Tf, \epsilon} \left[ \left(F - i T_{A1} \dot{F} - \frac{1}{2} (T_{A2})^{2} \ddot{F} \right) \right] (t_{f}) \,.
\end{align}
\end{subequations}

In the following, it will be convenient to introduce error estimates built from the Taylor-like series~\eqref{eq:resulttaylorPsi},~\eqref{eq:resulttaylorA} and~\eqref{eq:resulttaylordelay}. We simply define  this error estimates at a certain level of approximation as the magnitude of the first term ignored in the original Taylor series. Thus we define, with $G(f,t) = F(t) e^{-2i\pi f d(t)}$,
\begin{subequations}\label{eq:deffom}
\begin{align}
	\epsilon_{\Psi 2} &\equiv \frac{1}{2} \Tf^{2} \left| \frac{1}{G}\partial_{tt}G \right| \,, \\
	\epsilon_{A 1} &\equiv T_{A1} \left| \frac{1}{G} \partial_{t} G \right| \,, \\
	\epsilon_{A 2} &\equiv \frac{1}{2} T_{A2}^{2} \left| \frac{1}{G} \partial_{tt}G \right| \,, \\
	\epsilon_{d} &\equiv \frac{1}{2\pi} \left| \frac{1}{G} \partial_{tf} G \right| \,,
\end{align}
\end{subequations}
where the function $G$ and its derivatives are evaluated at $(f, t_{f})$. Reaching $\epsilon \simeq 1$ will indicate a breakdown of the perturbative approach. \SM{[expand a bit]}

@@

Using the Newtonian-order expressions~\eqref{eq:timescalesN} for the signal-dependent timescales $\Tf$ and $T_{A1}$, we can obtain a useful order-of-magnitude estimate for the error measures $\epsilon$ introduced in~\eqref{eq:deffom}. Higher-order amplitude terms beyond the first one in~\eqref{eq:resulttaylorA} will turn out to be completely negligible in the LISA case and we will ignore them in the following. We will present these estimates separately for the orbital response~\eqref{eq:transferOlocal} and the constellation~\eqref{eq:transferclocal}, as the different baseline of the delays (orbital radius $R$ or armlength $L$) as well as the presence of a time-varying prefactor $F(t)$ both affect the result. As we will see, when estimating the magnitude of the relevant derivatives of $G$ we have to take into account delay factors of the type $2\pi f d$.

@@

\subsection{Slowly chirping binaries and Direct approach for periodic modulations and delays}\label{subsec:comblisa}

In the LISA case, the modulations and delays entering~\eqref{eq:yslr} are periodic, with a period of one year and a frequency $f_{0} = 1/\mathrm{yr} \simeq 3.2\times 10^{-8}\mathrm{Hz}$. If the above perturbative formalism cannot be applied, we can still exploit this periodic structure to transform the . \SM{[]}
\be
	G(f,t) = \sum_{n} c_{n}(f) e^{-in\Omega_{0}t} \,.
\ee
